Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
subsections in paradigm section

\section{Experimental paradigm}
\label{sec:paradigm}

In principle, the family of DPM measures may be implemented with
any parser that generates a dependency graph (a single labelled arc
for each word, pointing to its head-word). Prior work
\cite{owczarzak07labelleddepseval} on related
measures has used an LFG parser \cite{cahill04lfg} or
an unlabelled dependency tree \cite{liu05syntaxformteval}.

@@

>>>>

\section{Experimental paradigm}
\label{sec:paradigm}
In this section, we outline the details of the implementation and
experimental variables explored in the experiments presented here.

\subsection{Parse tree implementation}
In principle, the family of DPM measures may be implemented with
any parser that generates a dependency graph (a single labelled arc
for each word, pointing to its head-word). Prior work
\cite{owczarzak07labelleddepseval} on related
measures has used an LFG parser \cite{cahill04lfg} or
an unlabelled dependency tree \cite{liu05syntaxformteval}.

@@

\subsection{Dimensions of metric family}
